### 2021-02-16 introduction.tex
add a new command that refers to the Bao et al. study

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

>>>>

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

### 2021-02-16 setup.tex
add a new command that refers to the Bao et al. study

 \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?

 \item What is the effective performance of each test generation tool, in terms of the number of detected malware, in the Bao et al. study, disregarding the DroidFax
  static analysis algorithms?

@@

Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation performance of test generation tools for mining sandboxes,
as reported by Bao et al., which might introduce a possible threat to their conclusions. Answering the third research question
allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
dynamic analysis through the use of static analysis algorithms.

We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work. Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.

The other $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation. Since Monkey was developed for stress testing, and can not perform text input, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

>>>>

 \item What is the impact of the DroidFax static analysis algorithms in the \blls?

 \item What is the effective performance of each test generation tool, in terms of the number of detected malware, in \blls, disregarding the DroidFax
  static analysis algorithms?

@@

Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation performance of test generation tools for mining sandboxes,
as reported in \blls, which might introduce a possible threat to their conclusions. Answering the third research question
allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
dynamic analysis through the use of static analysis algorithms.

We conducted two studies to answer the research questions above. First we performed a non-exact replication of the \blls. Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.

The other $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation. Since Monkey was developed for stress testing, and can not perform text input, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.
